Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-05-09 manuscript/article.Rmd
stable states overlay plot

`
```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS("working/sim data/ss_res_2.RDS")
ss_var <- ss_sim_data[43,]
p2  <- plot_ss_result1(ss_var$ss_res[[1]],
                ss_var$CB_var_gmax_s,
                ss_var$CB_var_h_s,
                ss_var$SB_var_gmax_s,
                ss_var$SB_var_h_s,
                ss_var$PB_var_gmax_s,
                ss_var$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

@@

>>>>

`
```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
ss_var <- ss_sim_data[20,]
p2  <- plot_ss_result1(ss_var$ss_res[[1]],
                ss_var$CB_var_gmax_s,
                ss_var$CB_var_h_s,
                ss_var$SB_var_gmax_s,
                ss_var$SB_var_h_s,
                ss_var$PB_var_gmax_s,
                ss_var$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r}
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_2.RDS"))
ss_novar <- ss_sim_data[22,]

ss_sim_data <- readRDS(here("simulations/sim data/ss_res_3.RDS"))
ss_var <- ss_sim_data[20,]

ss_result1 <- ss_novar$ss_res[[1]]
ss_result2 <- ss_var$ss_res[[1]]

p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
                             ss_var$ss_res[[1]],
                             xlims = c(-3, -2.25))

p_overlay
```

@@

https://onlinelibrary.wiley.com/doi/10.1111/ele.13760?af=R
